Notes

### 2024-11-18 notes.qmd
feat: add notations

>>>>

## Notation

Data Level

-   l0: unprocessed

-   l1: cleaned data, fill null value, add useful columns

-   l2: time-averaged data

### Columns naming conventions

-   `v_{x,y,z}` or `sw_vel_{X,Y,Z}`: solar wind plasma speed in the *ANY* coordinate system, in units of $km/s$

    -   `sw_vel_{r,t,n}`: solar wind plasma speed in the RTN coordinate system, in units of $km/s$
    -   `sw_vel_gse_{x,y,z}`: solar wind plasma speed in the GSE coordinate system, in units of $km/s$
    -   `sw_vel_lmn_{x,y,z}`: solar wind plasma speed in the LMN coordinate system, in units of $km/s$
        -   `v_l` or `sw_vel_l`: abbreviation for `sw_vel_lmn_1`
        -   `v_mn` or `sw_vel_mn` (deprecated)

-   `radial_distance`: radial distance of the spacecraft, in units of $AU$

-   `sw_elevation`: solar wind elevation angle, in units of $\degree$

-   `sw_azimuth`: solar wind azimuth angle, in units of $\degree$

-   `b_rtn_{x,y,z}` or `b_{r,t,n}`: magnetic field in the RTN coordinate system

-   `b_gse_{x,y,z}`: magnetic field in the GSE coordinate system

-   `model_b_{r,t,n}`: modelled magnetic field in the RTN coordinate system

-   `state` : *1* for *solar wind*, *0* for *non-solar wind*
